Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) }

### 2021-05-03 paper/paper.tex
Add some related work on synthesis
Add contig types
Add sections and contig content
Add draft of component specification
Add abstract
Add acknowledgement section

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{
Konrad Slind, 
Junaid Babar, and 
Isaac Amundson}
\IEEEauthorblockA{
Trusted Systems Group   \\
Collins Aerospace       \\
Minneapolis, Minnesota  \\
}
\and
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
}

@@

\section{Introduction}
\input{intro}

\section{Simple Example}
\input{example}

\section{Specification Language}
\input{specification}

\section{Verified Synthesis}
\input{synthesis}

\section{OSATE Integration for AADL}
\input{aadl-agree-osate}

\section{Conclusion}
\input{conclusion}

@@

% references section
\bibliographystyle{IEEEtran}
\bibliography{paper}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\konst}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\imp}{\Rightarrow}
\newcommand{\lval}{\ensuremath{\mathit{lval}}}
\newcommand{\set}[1]{\ensuremath{\{ {#1} \}}}
\newcommand{\kstar}[1]{\ensuremath{{#1}^{*}}}
\newcommand{\Lang}[1]{\ensuremath{{\mathcal L}({#1})}}
\newcommand{\LangTheta}[1]{\ensuremath{{\mathcal L}_{\theta}({#1})}}
\newcommand{\itelse}[3]{\mbox{$\mathtt{if}\ {#1}\ \mathtt{then}\ {#2}\ \mathtt{else}\ {#3}$}}

\newcommand{\figref}[1]{Fig.~\ref{#1}}

% Latex trickery for infix div operator, from stackexchange

\makeatletter
\newcommand*{\bdiv}{%
  \nonscript\mskip-\medmuskip\mkern5mu%
  \mathbin{\operator@font div}\penalty900\mkern5mu%
  \nonscript\mskip-\medmuskip
}
\makeatother

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\etal}{\textit{et al.}}
\newcommand{\etc}{\textit{etc.}}
\newcommand{\adhoc}{\textit{ad hoc}}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{
Konrad Slind, 
Junaid Babar, 
Isaac Amundson, and
David Hardin}
\IEEEauthorblockA{
Trusted Systems Group   \\
Collins Aerospace       \\
Minneapolis, Minnesota  \\
}
\and
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
}

@@

% \section{Introduction}
% \input{intro}

% \section{Simple Example}
% \input{example}

\section{System Model and Semantics}
\input{system}

% \section{Contiguity Types}
% \input{contig}

% \section{Filters}
% \input{filters}

% \section{Monitors}
% \input{monitors}

% \section{OSATE Integration for AADL}
% \input{aadl-agree-osate}

% \section{Related Work}
% \input{related-work}

% \section{Conclusion}
% \input{conclusion}

\section*{Acknowledgments}
This work is funded by DARPA contract HR00111890001. The views, opinions and/or findings expressed are those of the authors and
should not be interpreted as representing the official views or policies of the Department of Defense or the U.S. Government.

@@

% references section
% \bibliographystyle{IEEEtran}
% \bibliography{paper}
\end{document}
